### 2014-01-11 docs/reports/finalreport/architecture.tex
rivising report based on Mihai's feedback

\section{Architecture and Design}
The system is designed based on DDD (Data Driven Design) and Multi-Layer Architecture. As it is depicted in Figure \ref{fig:architecture}, the system is consisted of three main layers : Interface, Business and Data Access Layer. Data is passed between the layers using Model objects.

Interface layer can be divided into two main parts. Server side and client side. Server side which is denoted as Application Layer is following MVVC (Model-View, View, Controller) design model. It's main purpose is mapping Model-View objects of Interface Layer to Model objects and passing them to Business Layer and vice verse. Client side web pages are designed based on MVVM (Model-View, View, Model) model. Tools used for applying the model are explained in Section\ref{sec:tools}.

Using AOP (Aspect-Oriented Programming), logging, error handling and security are designed on top of other layers.

>>>>

\section{Architecture and Design}
\label{sec:architecture}
The system is designed based on DDD (Data Driven Design) and Multi-Layer Architecture. As it is depicted in Figure \ref{fig:architecture}, the system consists of three main layers : Interface, Business and Data Access Layer. Data is passed between the layers using Model objects.

Interface layer is divided into two main parts. Server and client side. Server side which is denoted as Application Layer is following MVVC (Model-View, View, Controller) design model. Its main purpose is mapping Model-View objects of Interface Layer to Model objects and passing them to Business Layer and vice versa. Client-side web pages are designed based on MVVM (Model-View, View, Model) model. Tools used for developing the model are explained in Section \ref{sec:tools}.

Using AOP (Aspect-Oriented Programming), logging, error handling and security systems are designed on top of other layers.

### 2014-01-11 docs/reports/finalreport/development.tex
rivising report based on Mihai's feedback

\section{Development}
In this section, some special issues related to development of different components are described.

\subsection{Order}
Ordering page is a full client-side page following the idea of SPA (Single Page Application) using KnockoutJS and BreezeJS. Complex business of the company in applying query, offering translators and purchasing order urges using design models and standards.
\subsection{Machine Learning's Data Accumulating}
In order to tackle the problem of translator's ranking, a data accumulating system is designed. Similar to Order, based on query document it offers three translators and stores client's choice. The data gathered by the system is used in a Machine Learning program using Learning to Rank algorithms. It aims to discover the underlying pattern for proposing the translators. The details of the project is described in seminar lecture related to the project. In contrast to Order system, the system eliminates translator's picture and name which prevents bias in final answer by estimator and puts emphasis on the presented criteria.
\subsection{Text Matching}
Using Lucene, translator's documents are stored regarding to their languages. In order to achieve the final text matching value, the similarity between each document and query document is calculated. The main problem here is the way to  aggregate result scores. As the problem is addressed in Seminar lecture, GP2\cite{gp2} algorithm is implemented.
\subsection{Translation Memory}
As it's mentioned before, the aim of Translation Memory system is helping the translators to exploit their previous-translated texts in their new translations. In order to develop the system, first HunAlign library is used for aligning the sentences of one text with the sentences of its corresponding text in another language. Although the algorithm is very error-prone specially for complex texts, adding dictionary and using rather simple and straightforward texts lead to more reasonable results. At the end, Lucene indexes the text and provides searching abilities.

>>>>

\section{Development}
\label{sec:development}
In this section, some special issues related to development of different components are described.

\subsection{Order}
Ordering page is a full client-side page following the idea of SPA (Single Page Application) using KnockoutJS and BreezeJS. By applying MVVM model, the data submitted in each step is stored in View-Model and used in the next steps. The system screen-shots of ordering process are shown in Figure\ref{fig:order-1}, Figure\ref{fig:order-2} and Figure\ref{fig:order-3}.  The payment process shown in Figure\ref{fig:order-3} is verified by a third-party service which supports different payment cards.

\subsection{Machine Learning's Data Accumulating}
In order to tackle the problem of translators ranking, a system similar to Order is designed. The system aims to accumulate data for Learning To Rank process. Based on query document, it offers three translators and stores client's (evaluator's) choice. In contrast to Order system, it eliminates the pictures and names of translators which prevents bias in final answers by estimators and puts emphasis on the presented criteria. A screen-shot of the system related to selecting the translators is shown in Figure\ref{fig:dataaccumulating}. In the next step, the data gathered by the system is applied on Learning to Rank algorithms which aim to discover the underlying pattern for proposing the best translators. The details of the project is described in seminar lecture related to the project.

\subsection{Text Matching}
Using Lucene, the documents of translators are categorized, indexed and stored based on their languages. In order to achieve the final text matching value, the similarity between each document and query document is calculated. The main problem here is the way to  aggregate result scores. As the problem is addressed in Seminar lecture, GP2\cite{gp2} algorithm is implemented.

\subsection{Translation Memory}
As it is mentioned before, the aim of Translation Memory system is helping the translators to exploit their previous-translated texts in their new translations. In order to develop the system, first HunAlign library is used for aligning the sentences of one text with the sentences of its corresponding text in the other language. While the algorithm tends to be error-prone in its basic version for complex texts, by extending dictionary and using rather simple and straightforward texts, reasonable aligned sentences were achieved. At the end, Lucene indexes the text and provides searching abilities.

\subsection{Scheduling}
The system is also designed following the SPA idea and using Java-Script libraries and Web-API. Figure\ref{fig:scheduling} depicts the schedule of an arbitrary translator.

\subsection{Chat}
Using Signal-R capabilities, the Chat system is designed and developed. Related interfaces for meeting room as well as chatting with help-desk user are shown in Figure\ref{fig:chat}.

\begin{figure}[h]
\begin{center}
\includegraphics[scale=\figurescaling]{figures/order-1.jpg}
\caption{Order - entering primitive data
\label{fig:order-1}}
\includegraphics[scale=\figurescaling]{figures/order-1.jpg}
\caption{Order - selecting translator
\label{fig:order-2}}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[scale=\figurescaling]{figures/order-1.jpg}
\caption{Order - payment process
\label{fig:order-3}}
\includegraphics[scale=\figurescaling]{figures/order-1.jpg}
\caption{Data Accumulating - selecting translator
\label{fig:dataaccumulating}}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[scale=\figurescaling]{figures/chat.jpg}
\caption{Scheduling
\label{fig:scheduling}}
\includegraphics[scale=\figurescaling]{figures/chat.jpg}
\caption{Chat system
\label{fig:chat}}
\end{center}
\end{figure}

### 2014-01-11 docs/reports/finalreport/introduction.tex
rivising report based on Mihai's feedback

Using the platform, regardless to geographical location of translators and clients, they can communicate and proceed a translation process. It aims to ease translating text to even not-so-popular languages as well as reduction of final cost.

In the following, first I describe system requirements. Then system architecture and design are explained. Tools and Technologies applied in the platform are Section \ref{sec:tools}. At the end, some special issues during system development are reported in the last section.

>>>>

Using the platform, regardless of geographical location of translators and clients, they can communicate and proceed with translation. It aims to ease translating text to even not-so-popular languages as well as reduction of final cost.

The developed platform mainly consists of two parts. First, storing profiles of translators by providing registration as well as scheduling possibilities. Additionally, assisting them during translation process by offering a simple translation memory system. Second, providing a platform for clients to search and hire the translators and purchase the orders. Some complexities like text processing and expert ranking are tackled in the second part.

The remain of the report is organized as follows: In Section \ref{sec:scenario}, system requirements and usual scenarios are described in detail. Then in Section \ref{sec:architecture}, system architecture as well as design methods are explained. Applied tools and technologies following with a short description are introduced in Section \ref{sec:tools}. At the end in Section \ref{sec:development}, by demonstrating the final product in some screen-shots, specific issues in system development are reported.

### 2014-01-11 docs/reports/finalreport/problem.tex
rivising report based on Mihai's feedback

\section{Requirements and Scenario}
In the first step, Translators define their profiles. Each translator is setting a price and duration per word for each language pair. Then, they upload the documents which has been translated before. These documents are used for calculating the similarity.

In order to search for a translator, the client uploads documents to the website. Based on four criteria, the system starts searching the best three translators. These criteria are cost, delivery time, frequent cooperation and text matching. Every criterion has also its weight which defines its importance from client's point of view.

Final cost is calculated based on price per word. Delivery time is estimated using the schedule of translator as well as duration per word. Finally, in order to find text matching value, the similarity between query document and previous translated documents is aggregated.

After merging the results of different criteria, the system represents the most appropriate translators to the client. By choosing the translator and following payment process, the translator is informed for starting translation. After finishing translation, a qualified proof-reader chosen by client revises the text and may send some corrections to the translator. At the end the proof-reader rates the translation.

The requirements considered in the project are as follows:
\begin{itemize}
	\item wizard-like page for ordering process in a SPA (Single Page Application) structure.
	\item Indexing previous-translated texts and finding an aggregation function for their similarity values regarding to query document.
	\item Developing a ranking function in order to find the best three translators among all.
	\item Calculating delivery time based on translator's schedule.
	\item Web as well as Web API interface.
	\item Payment process.
	\item Short response time.
	\item Considering different languages and timezones.
\end{itemize}

>>>>

\section{Scenario and Requirements}
\label{sec:scenario}
In this section, first the usual system scenario is described in detail. Then, some specific requirements related to system development are specified.

By registering in the platform, the translators start to declare their profiles. Regarding to each language pair, the price and duration per word is set. In the next step, the translators upload their previous-translated documents. The documents are processed and used in text matching as well as  translation memory systems. As the last step, the translators fill the time table using schedule system. They specify the time slots in which they are ready to work and potentially can be hired by clients.

The client starts searching for translators by uploading a document. Based on four criteria, the system searches and retrieves the three most-related translators. These criteria are cost, delivery time, frequent cooperation and text matching. Related to each criterion, a weight is defined which specifies importance of the criterion from client's point of view.

Using the profiles of the translators as well client's document, the value for each criteria is estimated. Cost is calculated based on price per word and the number of words in the document. Delivery time is estimated using the schedule of translator, duration per word as well as the number of words. Finally, text matching value is computed by processing the text and aggregating the similarity values between the query document and the previous-translated documents.

After achieving the values of different criteria, the system ranks the translators and represents the three most-related ones to the client. The client chooses one and follows payment process. By purchasing the order, the platform informs the translator and asks for confirmation. During translation, the client and translator are in contact using a chat system. After finishing translation, a qualified proof-reader chosen by client revises the text and may send some corrections to the translator. At the end, the proof-reader assesses the quality of translation from different points of view (grammar, style, accuracy, content and language).

The requirements considered in the project are as follows:
\begin{itemize}
	\item Wizard-like page for purchasing the order in a SPA (Single Page Application) structure.
	\item Indexing previous-translated texts and finding a function for aggregating their similarity values regarding to query document.
	\item Developing a ranking function in order to find the best three translators among all.
	\item Calculating delivery time based on translator's schedule.
	\item Web-Page as well as Web-API interface.
	\item Supporting payment process for different payment cards and methods.
	\item Short response time.
	\item Considering different languages and timezones.
\end{itemize}
